---
title: "Project 1"
author: "Stefanee Tillman"
date: "9/25/2021"
output: github_document
---

```{r, eval = FALSE}
rmarkdown::render("C:/Users/Stefa/OneDrive/Documents/GitHub/Project1new/Project1new.rmd",
 output_format = "github_document",
 output_options = list(
 toc = FALSE,
 toc_depth = 3,
 number_sections = FALSE,
 df_print = "default",
keep_html = FALSE
))
```

```{r, eval = FALSE, message=FALSE}
require("httr")
require("jsonlite")
require("dplyr")

my_url<- paste0("https://api.covid19api.com/summary")
my_result<- httr::GET(my_url)
str(my_result)
my_content<- httr::content(my_result, as = 'text')
my_content_json<- jsonlite::fromJSON(my_content)
str(my_result$content)

data<- rawToChar(my_result$content)
coviddata<- fromJSON(data)
str(coviddata)
```

# Required Packages

In this section shows the required packages needed to create this project.

• `rmarkdown()` to convert rmarkdown using the render() function.

• `knitr()` produces flexible designs and finer control of graphics.

• `tidyverse()` to generate plots, use chaining/piping, and manipulate data. 

• `jsonlite()` to convert between JSON data and R objects.

• `vignette()` to view and display vignette.


